---
title: "Statrozphere Volume I"
author: "Kadek Adit Wiryadana"
date: "2/10/2021"
output: html_document
---

```{r  include = FALSE}
library(tidyverse)

current_date <- Sys.Date()
```
# Statrozphere
### A daily plot for **#rstater** in Instagram & Twitter

We will explore the possibility of R native graphic engine, ggplot2, lattice, plotly, and our creativity. Our aim is to demonstrate that R, a free and open source software, could produce an attractive yet a reproducible plot. Not to mention this is a way to force me (author) to learn R, otherwise I will always procrastinate. I will do it in small steps at a time, at least one plot at a time (hopefully).

We will use a biomedical data (primarily), as I am a medical doctor. Familiarity of the data arent neccesarry, but it helps a lot during early learning phase. First we will use the data obtained from [Kaggle](https://www.kaggle.com/uciml/pima-indians-diabetes-database?search=diabetes)

## Volume I Issue 1   
`r current_date` @ Puskesmas Tabanan III

Our topics is a simple scatter plot and regression line. We will explore the relathionship of Blood Glucose Levels and BMI.
```{r read_data}
dm <- read.csv("diabetes.csv", na.strings = c("NA", "0")) #string NA and 0 are considered NA
dm$Outcome <- ifelse(is.na(dm$Outcome), 0, 1)
#glimpse(dm)
pairs(dm)
```

```{r scatterplot1}
dm$Glucose = jitter(dm$Glucose)
dm$Insulin = jitter(dm$Insulin)

alpha = 150 # Transparent points
palette(c(rgb(200, 79, 178, alpha = alpha, maxColorValue = 255), rgb(105, 147, 45, alpha = alpha, maxColorValue = 255)))
         

#par(mar=c(3,3,2,1),
    #mgp = c(2,0.4,0),
    #las = 1,
    #tck = -.01,
    #xaxs = "i", yaxs = "i")              
              
plot(dm$Glucose, dm$Insulin, 
     #bg=ifelse(dm$Outcome==0, "gray", "steelblue"), 
     #bg=dm$Outcome,
     bg=ifelse(dm$Outcome==0, rgb(200, 79, 178, alpha = alpha, maxColorValue = 255), rgb(105, 147, 45, alpha = alpha, maxColorValue = 255)),
     pch=21, 
     cex=0.9,
     main ="Relathionship of Glucose & Insulin Levels",
     #sub = "UCI Machine Learning Data - Pima Indian Diabetes Database",
     ylab = "Insulin Levels",
     xlab = "Glucose Levels",
     ylim = c(0,1000),
     xlim = c(50,200),
     axes = FALSE,
     frame.plot = FALSE)
     #panel.first = abline (h=seq(2, 4.5, 0.5), col = "grey80"))

legend(x=50, y= 900,
       legend = c("0","1"), 
       #col = dm$Outcome, 
       col = c(rgb(200, 79, 178, alpha = alpha, maxColorValue = 255), rgb(105, 147, 45, alpha = alpha, maxColorValue = 255)),
       pch=16)

at = pretty(dm$Glucose)
mtext(side = 1, text = at, at = at,
      col = "grey20", line = 1, cex = 0.9)

at = pretty(dm$Insulin)
mtext(side = 2, text = at, at = at, col = "grey20", line = 1, cex = 0.9)

text(165, 730, "Good Outcome", col = rgb(200, 79, 178, maxColorValue = 255))
text(122,650, "Poor Outcome", col = rgb(105, 147, 45, maxColorValue = 255))


#scatter1b <- plot(dm$BMI, dm$BloodPressure)
#scatter1c <- plot(dm$BMI, dm$SkinThickness)
```






